---
title: "RestoreNet GLMMs, Tables S3 through S10"
author: "Lia Ossanna"
date: "2024-11-25"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
library(tidyverse)
library(glmmTMB)
library(performance)
library(DHARMa)
load("../RData/13.1_generalized-linear-models_subplot-Count_final.RData")
load("../RData/13.2_generalized-linear-models_2x2-Seeded-Cover_final.RData")
```


## Description of variables
Response variables:
- `Count`: Number of individuals per 0.0625 m^2^, the size of the subplots.
- `Cover`: Percent cover.


## Table S3. Density of Sonoran Desert desirable species
```{r}
summary(nb.sonoran.des)
r2(nb.sonoran.des)
```
  

## Table S4. Density of Sonoran Desert weedy species
```{r}
summary(nb.sonoran.weed)
r2(nb.sonoran.weed)
```
  

## Table S5. Density of Sonoran Desert seeded species
```{r}
summary(nb.sonoran.seed)
r2(nb.sonoran.seed)
```

Table S6. Cover of Sonoran Desert seeded species
```{r}
summary(pos.sonoran.seed)
r2(pos.sonoran.seed)
```


## Table S7. Density of Northern Arizona desirable species
```{r}
summary(nb.naz.des)
r2(nb.naz.des)
```

## Table S8. Density of Northern Arizona weedy species
```{r}
summary(nb.naz.weed)
r2(nb.naz.weed)
```

## Table S9. Density of Northern Arizona seeded species
```{r}
summary(nb.naz.seed)
r2(nb.naz.seed)
```

## Table S10. Cover of Northern Arizona seeded species
```{r}
summary(pos.naz.seed)
r2(pos.naz.seed)
```

